RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-18 doc/paper.tex
Work on Section 3.2

\section{Proposed iterated local search method}\label{sec:rils}

@@

   \begin{algorithm}
  		\begin{algorithmic}[1] 
  			 \State \textbf{Input}: a COP problem; an LS procedure  
  	 		\State \textbf{Output}: an approximate (feasible) solution 
  	 		\State $s \gets$ Generate an initial solution
  	 		\State  $s \gets LS(s)$
   	 		\While{\emph{Stopping criteria is not met}}
   	    		 \State  $s' \gets$ Perturbation($s$)
   	    		 \State  $s' \gets$ LS($s'$)
   	    		 \State  $ s \gets$ AcceptanceCriterion($s, s'$)
   	 		\EndWhile
   		\end{algorithmic}
    	\caption{An ILS framework from the literature.}
    	   	     \label{alg:ils}
    \end{algorithm}

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated. Secondly, the perturbed solution is then improved by LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.

   \subsection{Ordinary least square method}

   \subsection{The proposed Rils-Rols}

\section{Experimental evaluation}\label{sec:experiments}

>>>>

\section{Proposed iterated local search method}\label{sec:rils}
   Before we give details on our \textsc{Rils-Rols} method fro solving SR, we explain the basics of the two main techniques incorporated into our algorithm. These are ILS meta-heuristic and OLS methods, respectively.

@@

   \begin{algorithm}
  		\begin{algorithmic}[1] 
  			 \State \textbf{Input}: a COP problem; a LS procedure  of the problem 
  	 		\State \textbf{Output}: an approximate (feasible) solution 
  	 		\State $s \gets$ Generate an initial solution
  	 		\State  $s \gets LS(s)$
   	 		\While{\emph{Stopping criteria is not met}}
   	    		 \State  $s' \gets$ \texttt{Perturbation}($s$)
   	    		 \State  $s' \gets$ \texttt{LS}($s'$)
   	    		 \State  $ s \gets$ \texttt{AcceptanceCriterion}($s, s'$)
   	 		\EndWhile
   		\end{algorithmic}
    	\caption{An ILS framework from   literature.}
    	   	     \label{alg:ils}
    \end{algorithm}

An initial solution may be generated randomly or by using a greedy heuristic, which is afterwards, improved by LS procedure. At each iteration, ILS applies three steps. First, the current incumbent solution is perturbed, that is mutated in a way the knowledge of the current best solution is (partially) used at the next iterations.  Secondly, the perturbed solution is then improved by LS procedure. Thirdly, the LS outcome is thereafter compared to the incumbent solution and possibly replaced as the new one, with accordance to the chosen acceptance criterion.

 \subsection{Ordinary least square method}
   Ordinary least square method (OLS) is a linear regression technique. It is based on applying the least-square method to minimize the square residual (error) sum  between actual and predicted values (given by the model). More precisely, given data $({X}, y)$, the task is to determine linear mapping $\tilde{y} = k \textbf{x} + b$, that is coefficients (line slope) $k = (k_1, \ldots, k_n)$ and $b$ (intercept), so that $ \sum_{i} |\tilde{y}_i - y_i|^2 $ is minimized. This sum is also know by the term the sum of squared error (SSE). There are many methods to minimize SSE; one of the analytical methods is the calculus method that takes into account   partial derivation w.r.t.  $k$ of the cost function $ \sum_{i} |\tilde{y}_i - y_i|^2 $, getting

   $$  \frac{\partial}{\partial k} \sum_{i} |\tilde{y}_i - y_i|^2 = \frac{\partial}{\partial k} \sum ( kx_i+b  - y_i)^2 =  \sum -2x_i(kx_i + b - y_i)  =  \sum -2x_i (\tilde{y}_i - y_i ) . $$

   Taking into account   partial derivation w.r.t.  $b$, we have 
    $$  \frac{\partial}{\partial b} \sum_{i} (\tilde{y}_i - y_i)^2  = \frac{\partial}{\partial b} \sum ( kx_i+b  - y_i)^2 = \sum -2  (\tilde{y}_i - y_i). $$

    Thus, we get the system of equation: 
    \begin{align*}
    	  &\sum -2x_i (\tilde{y}_i - y_i )  = 0 \\
    	  &\sum -2  (\tilde{y}_i - y_i ) = 0.
    \end{align*}
     The above system can be transformed to 
     \begin{align*}
     	 & \sum y_i \cdot x_i   = b\sum x_i \cdot x_i  +  k \cdot \sum x_i \\
     	 & \sum y_i  = k \sum x_i + b \cdot n 
     \end{align*}
     which is a system of two equations with two variables ($k$ and $b$) that is  solved efficiently.
   \subsection{The proposed Rils-Rols}
    \fxnote{TODO}
\section{Experimental evaluation}\label{sec:experiments}
